# Code for reading in the dataset and/or processing the data
```{r echo=TRUE}
data1<-read.csv("activity.csv")
summary(data1)
```
## mean total number of steps taken per day.
```{r}
stepsbyday <- tapply(data1$steps, data1$date, sum, na.rm=TRUE)
```
###  Histogram of the total number of steps taken each day
```{r echo=TRUE}
hist(stepsbyday)
```
### mean and medain of step each day
```{r echo=TRUE}
mean(stepsbyday)
median(stepsbyday)
```
### Average daily activity pattern?
```{r echo=TRUE}
average <- aggregate(x=list(meanSteps=data1$steps), by=list(interval=data1$interval), FUN=mean, na.rm=TRUE)
```
#####  Time series plot
```{r echo=TRUE}
plot(average$interval,average$meanSteps,type="l")
```
### get max value
```{r echo=TRUE}
max<- which.max(average$meanSteps)
```
#####  The total number of missing values in the dataset 

```{r}
numMissingValues <- length(which(is.na(data1$steps)))
```
### remove NA value and create new data set
```{r echo=TRUE}
data2<-na.omit(data1)
#data2[1]<-mean(data2$steps,na.rm=TRUE)

```
#####  Histogram of the total number of steps taken each day 
```{r echo=TRUE}
stepsByDayImputed <- tapply(data2$steps, data2$date, sum)
hist(stepsByDayImputed)
```
### get mean and medain
```{r echo=TRUE}
stepsByDayMeanImputed <- mean(stepsByDayImputed)
stepsByDayMedianImputed <- median(stepsByDayImputed)
```
### weekend or week day
```{r echo=TRUE}
data2$dateType <-  ifelse(as.POSIXlt(data2$date)$wday %in% c(0,6), 'weekend', 'weekday')
```
#####  Panel plot containing a time series plot
```{r echo=TRUE}
averagedActivityDataImputed <- aggregate(steps ~ interval + dateType, data=data2, mean)
plot(averagedActivityDataImputed$interval,averagedActivityDataImputed$steps,type="l")  
  
```